---
title: "HW - Project Organization"
author: Dinelka Nanayakkara
date: "October 7, 2024"
output:
  pdf_document:
    number_sections: true


---

<br>

```{r libraries, echo=FALSE, message=FALSE}
library(gt)
library(tidyverse)
```

# Git Respository
The git repository can be found here: https://github.com/dinelka97/BIOS-611-Project.

# Data Description
The dataset used for this project relates to loan approval rates. The primary goal of using this data 
would be to build a model that could predict if an individual gets approved for a loan or not. Although 
supervised learning will be the primary task of this project, I aim to also perform unsupervised learning
to explore patterns that might be in the data.

## Variables

The following table provides a brief overview of the variables used in the dataset.

```{r, include=FALSE}
data <- read_csv("src_data/train.csv")

labels <- c(
  "Unique identifier", "Age", "Income level", 
  "Home ownership status (own, rent, mortgage, other)",
  "Length of employment", "Purpose of obtaining loan", 
  "Credibility of loan", "Loan amount", "Loan interest rate",
  "Loan amount as a percentage of income", "Default indicator",
  "Length of credit history", "Loan Approval Status"
)

d_type <- c(
  "num", "num", "num", "categorical", "num", "categorical",
  "categorical", "num", "float", "float", "categorical", "numeric",
  "categorical"
)

vars <- data.frame(
  var_name = colnames(data), label = labels, data_type = d_type
)
```

```{r, echo=FALSE}
vars %>%
  gt() %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels()
  )
```


## Objectives

I plan to work on the following as part of the project:

* If we consider person_home_ownershipm person_emp_length, and person_income as one variable - can we build clusters based on this?
* Does a past credit default decrease the possibility of loan approval by a great extent?
* Can we classify loan amounts and credibility of an individual?
* I hypothesize that those with a low income do not have a good credit history and they are more prone to apply for loans, thus having a longer credit history.
* Build a model using logistic regression, random forest, and neural networks to predict if a loan is approved or not.

